---
title: "Developing Data Products"
subtitle: "Course Project 1"
author: "Aubin Bannwarth"
date: "09/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```
## Summary

This webpage was constructed for the first project in the *Developing Data Products* course on Coursera. We describe below how we created a map using `leaflet` to display the locations of places of worship in the United States.


## The data set

I will be using [an openly available dataset](https://data.world/awram/us-places-of-worship) that contains information about around 50 000 **places of worship** in the United States. The latitude and longitude of each place of worship are provided, which will allow us to show their position on a map of the US using `leaflet`.

One must create an account with [data.world](https://data.world/) to access the data set, which can then be downloaded as a *.csv* file. We can also [configure RStudio and data.world](https://data.world/integrations/r-and-r-studio) to allow us to retrieve the data using SQL queries. 

The code below does this, selecting the `name`, latitude `y`, and longitude `x` columns from the `All_Places_of_Worship` table in the `worship_ds` dataset. Note also that we first load the `data.world` package, then configure it with `set_config()`. The `cfg_saved()` function retrieves the default configuration that we have saved, with our private API Token.
```{r}
library(data.world)

set_config(cfg_saved())

worship_ds <- "https://data.world/awram/us-places-of-worship"

worship <- query(
  qry_sql("SELECT name, x, y FROM All_Places_of_Worship"),
  dataset = worship_ds
)

```

## Creating the Leaflet map
It's now just a matter of sending our `worship` data frame through the `leaflet()` pipeline, and we obtain the desired map:
```{r}
library(tidyverse)
library(leaflet)

worship_map <- worship %>%
  mutate(lat = y, lng = x) %>%
  select(-x, -y) %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions(),
             popup = worship$name
             )

worship_map
```

